---
title: "Computational Archaeology"
author: "Martin Hinz"
date: "HS 2019"
institute: "Institut für Archäologische Wissenschaften, Universität Bern"
output:
  xaringan::moon_reader:
    keep_md: true
    chakra: libs/remark-latest.min.js
    css: ["libs/default.css", "libs/default-fonts.css", "libs/customize.css"]
    lib_dir: libs
    seal: false
    nature:
      beforeInit: "libs/macros.js"
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      fig_caption: yes
---
class: title-slide
```{r, echo = FALSE}
# https://stackoverflow.com/questions/25646333/code-chunk-font-size-in-rmarkdown-with-knitr-and-latex
def.chunk.hook  <- knitr::knit_hooks$get("chunk")
knitr::knit_hooks$set(chunk = function(x, options) {
  x <- def.chunk.hook(x, options)
  ifelse(options$size != "normalsize", paste0("\\", options$size,"\n\n", x, "\n\n \\normalsize"), x)
})
```

```{r, echo = FALSE, results="asis"}
cat('## ', rmarkdown::metadata$title)
```
.small[
```{r, echo = FALSE, results="asis"}
cat('#### ', rmarkdown::metadata$author)
```

```{r, echo = FALSE, results="asis"}
cat(rmarkdown::metadata$institute)
```

```{r, echo = FALSE, results="asis"}
cat(rmarkdown::metadata$date)
```

### Presentations

- [01\. Session: Introduction](01_session/session_1_introduction.html) | 18/09/19
- [02\. Session: Your Computer as research tool](02_session/session_2_computer_as_research_tool.html) | 25/09/19
- [03\. Session: Data Bases I](03_session/session_03_database_1.html) | 02/10/19
- [04\. Session: Data Bases II](04_session/session_04_database_2.html) | 09/10/19
- 05\. Session: Visualisation I | 23/10/19
- [06\. Session: Visualisation II](06_session/session_06.html) | 30/10/19
- [07\. Session: Basic Statistics](07_session/session_07.html) | 06/11/19
- 08\. Session: 14C Calibration I | 13/11/19
- 09\. Session: 14C Calibration II | 20/11/19
- 10\. Session: GIS I | 27/11/19
- 11\. Session: GIS II | 04/12/19
- 12\. Session: Digital Documentation | 11/12/19
]

.tiny[
**Data**
The data base for the course exists in two formats (Firebird and HSQLDB). Please download and check which version is running on your operation system and Libre Office Version

- [Miskovice HSQLDB](miskovice.odb)
- [Miskovice Firebird](miskovice_firebird.odb)
]

.footnote[
.small[
<sup>\*</sup> You can find the **code of this presentations** at the [github repository](https://github.com/MartinHinz/ca_hs_2019). You might also like to check out the [**video tutorials** in english](https://tube.switch.ch/channels/503285f4) that will be made available.
]
]
