---
title: "Computational Archaeology"
subtitle: "01 - Introduction"
author: "Martin Hinz"
institute: "Institut für Archäologische Wissenschaften, Universität Bern"
fontsize: 9pt
date: "18/09/19"
output:
  xaringan::moon_reader:
    chakra: "../libs/remark-latest.min.js"
    css: ["../libs/default.css", "../libs/default-fonts.css", "../libs/customize.css"]
    lib_dir: "libs"
    seal: false
    nature:
      beforeInit: "../libs/macros.js"
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      fig_caption: yes
      ratio: "16:10"
---
class: title-slide, center, middle
```{r, echo = FALSE}
# https://stackoverflow.com/questions/25646333/code-chunk-font-size-in-rmarkdown-with-knitr-and-latex
def.chunk.hook  <- knitr::knit_hooks$get("chunk")
knitr::knit_hooks$set(chunk = function(x, options) {
  x <- def.chunk.hook(x, options)
  ifelse(options$size != "normalsize", paste0("\\", options$size,"\n\n", x, "\n\n \\normalsize"), x)
})
```

```{r, echo = FALSE, results="asis"}
cat('# ', rmarkdown::metadata$title)
```

```{r, echo = FALSE, results="asis"}
cat('## ', rmarkdown::metadata$subtitle)
```

```{r, echo = FALSE, results="asis"}
cat('### ', rmarkdown::metadata$author)
```

```{r, echo = FALSE, results="asis"}
cat('#### ', rmarkdown::metadata$institute)
```

```{r, echo = FALSE, results="asis"}
cat(rmarkdown::metadata$date)
```

---

## Schedule

```{r echo=FALSE}
library(magrittr)
library(kableExtra)
schedule <- c(
  "18/09/19", "Introduction", "Your Brain",
  "25/09/19", "General Aids", "Libre Office Writer, Zotero",
  "02/10/19", "Data Bases I", "Libre Office Base",
  "09/10/19", "Data Bases II", "Libre Office Base",
  "23/10/19", "Visualisation I", "Libre Office Calc",
  "30/10/19", "Visualisation II","Libre Office Calc",
  "06/11/19", "Basic Statistics", "Libre Office Calc",
  "13/11/19", "14C Calibration I", "OxCal/Chronomodel",
  "20/11/19", "14C Calibration II", "OxCal/Chronomodel",
  "27/11/19", "GIS I", "QGIS",
  "04/12/19", "GIS II", "QGIS",
  "11/12/19", "Digital Documentation", "Your Brain"
)
schedule <- as.data.frame(matrix(schedule,ncol=3, byrow = T))
colnames(schedule) <- c("date", "topic", "Software")
knitr::kable(schedule)  %>%
  kable_styling(bootstrap_options = c("striped", "hover"),
                latex_options = "striped",
                full_width = T)
```

---

## Software in this course

- free (and most of the time) open source software
- most basic software

.small[
### Libre Office

- free and open source (FOSS) office package
- most commands and procedures similar to 'the other' office package

### OxCal

- free, but not open source
- quasi standard in archaeology

### Chronomodel

- FOSS alternative to OxCal
- (have to figure out if we can use it instead)

### QGIS

- FOSS GIS package
- General ideas and concepts are transferable to 'the other' GIS software
]

---

## What is computational archaeology

### Topics<sup>*</sup>

1. The use of *digital data* in archaeological research.
2. The general *use of computers* in archaeological research.
3. The use of *computational algorithms to fill gaps in archaeological data* in ways that can’t be done with traditional techniques.
4. *Data mining* and *multidimensional analyses* of archaeological data.
5. The use of *simulation models and artificial intelligence* to understand the processes and dynamics of past societies.
6. The use of *computer visualizations* to create immersive *virtual* experiences of archaeological sites and materials

.footnote[[*] from http://isaacullah.github.io/What-is-Computational-Archaeology/]

---

## What is computational archaeology

### Fields<sup>*</sup>

1. **GIS and geospatial data analysis.**
2. **Digital imagery and photogrammetry.**
3. **Statistical computing and quantitative analysis.**
4. **Data visualization.**
5. Agent Based Modeling and simulation.
6. 3D modeling, virtual reality, and augmented reality.
7. Video gaming and digital animation.

We will touch the **highlighted** subjects.

.footnote[[*] from http://isaacullah.github.io/What-is-Computational-Archaeology/]

---

## Organisations that are related to Computational Archaeology

[Very subjective list]

* [CAA](https://caa-international.org)
* [ISAAK](https://isaakiel.github.io/)
* [ACA](http://aca.archaeological.science/)

---

## Other terms

* Cyber Archaeology
* Digital Archaeology
* Archaeoinformatics
* Digital Humanities

---
